\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\usepackage[left=2cm,top=2cm,right=2cm,bottom=2cm]{geometry}

\begin{document}
% Top Section (Name and Contact Info)
\noindent
\textbf{\Large SIDDHARTH SINGH} \\
+1(929) 689-4615 ⋄ New York, NY \\
sms10221@nyu.edu ⋄ Linkedin ⋄ GitHub ⋄ Portfolio

% Education
\medskip
\noindent
\textbf{EDUCATION}

\noindent
\textit{New York University | New York, NY} \\
\textit{September 2023 - May 2025 | Master of Computer Science | GPA: 3.61/4.0}

\noindent
\textit{SRM Institute of Science and Technology | Chennai, India} \\
\textit{July 2017 - May 2021 | Bachelor of Computer Science and Engineering | GPA: 8.10/10}

% Experience
\medskip
\noindent
\textbf{EXPERIENCE}

\noindent
\textit{Cognizant Technology Solutions | Google Cloud Engineer | Hyderabad, India | July 2021 - August 2023}
\begin{itemize}[itemsep=1pt]
    \item Increased team performance by 35\% through customer management, scalable system implementations, and cloud infrastructure management.
    \item Optimized cloud-native applications using BigQuery, Cloud Functions, and Firebase, improving operational efficiency by 40\%.
    \item Trained and mentored new hires on GCP, increasing their efficiency by over 50\%.
    \item Ensured a 99.9\% system availability rate for major clients including Spotify, Netflix and Bank of India.
\end{itemize}

\noindent
\textit{Webtech Infomedia Pvt Ltd. | Web Development Intern | Mumbai, India | June 2019 - August 2019}
\begin{itemize}[itemsep=1pt]
    \item Developed a web interface for smart device management using HTML, Bootstrap, Node.js, and Django.
    \item Implemented security protocols to enhance data integrity and mitigate security risks.
\end{itemize}

% Projects
\medskip
\noindent
\textbf{PROJECTS}

\noindent
\textit{Taleweaver}
\begin{itemize}[itemsep=1pt]
    \item Built an application using AWS Rekognition, OpenAI's GPT, and AWS Cognito for user authentication and session management.
    \item Hosted on AWS EC2, used AWS Lambda for serverless backend operations and DynamoDB for data storage.
\end{itemize}

\noindent
\textit{Serverless Dining Concierge Chatbot}
\begin{itemize}[itemsep=1pt]
    \item Developed a serverless, microservice-driven web application that provides restaurant suggestions.
    \item Utilized AWS S3, API Gateway, Lambda functions, and other services to develop various features.
\end{itemize}

% Skills
\medskip
\noindent
\textbf{TECHNICAL SKILLS}
\begin{itemize}[itemsep=1pt]
    \item \textit{Programming Languages:} Python, C, SQL, HTML, JavaScript, Java, Node, Django
    \item \textit{Database Systems:} Redshift, CloudSQL, Cloud Spanner, AlloyDB, BigQuery, BigTable, DynamoDB, RDS
    \item \textit{Certifications:} Professional Cloud DevOps Engineer, Associate Cloud Engineer, Deep Learning
    \item \textit{Other Technologies:} GCP, AWS, Docker, Kubernetes, Git, NumPy, Pandas, Tensorflow, Redis
\end{itemize}
\end{document}
```

This LaTeX document generates a one-page resume that reflects the given job description and considers more emphasis on Java, Node and Django in the technical skills section. Note that you need to compile this LaTeX code into a PDF (or other desired format) to view the final version of the document. Make sure your LaTeX compiler has the necessary packages installed.